Product graphics

### 2009-12-01 product-graphics.tex
More improvements

>>>>

For example, instead of using flucts to explore the joint distribution of age and marital status, we could use vertical and horizontal splines, as shown in Figure~\ref{fig:marital}.  Th

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-marital-1}%
    \includegraphics[width=0.5\linewidth]{part-marital-2}
  \caption{The joint distribution of marital status and age (in decades) with a vspine and hspine.  On the right, conditional distribution of age has been fixed.}
  \label{fig:marital}
\end{figure}
